%
\section{Physical device}\label{sec:device}
%
Developing with the emulator only will do you no good. You have to experience your program on a real device. Things that might look great on an emulator, may not even work on a real phone. It maybe just you fingers that are hiding the screen. Buttons are too small or too close.
%
%
\subsection{How to connect to SSH over usb connection from PC}
%
\begin{itemize}
\item the usb is either \verb,usb_storage, or \verb,usb_net,
\item enable developer mode
\item enable SSH (it's openssh, not dropbear)
\item set password
\item goto usb settings
\item change that to developer mode
\item reconnect usb cable
\item you should see the ip address of the device on the UI
\item you should be able to ssh to that address from PC (set an ip address first)
\end{itemize}
Taken from \cite{ex01}.

This section obviously needs a lot more information. Lacking a physical device or an SDK that enables me to interact with it, this has to be done in future.
%
%
\subsection{How do I deploy a package to my phone?}
%
As of now there is only the Alpha2 SDK out that has no built-in features to deploy a package to your device.

But you can help yourself\footnote{Since I have no device yet, I couldn't test this. Time will come, more details will follow.}:
%
\begin{enumerate}
\item build RPM
\item deploy RPM, look in the output for the location
\item copy RPM to Jolla phone
\item use \verb,pkcon install-local, to install it locally
\end{enumerate}
%
Also have a look at \cite{mer02}.
%